### 2021-04-14 input/experiments.tex
adapt text of experiments to new figures

\noindent We focus on the complexity of \NAME. We measure the average
number of messages generated per \process during the experiment; and
the time before reaching consistent partitioning after adding or
removing a partition.

@@

Figure~\ref{fig:complexity} shows the results of this experiment. The
top part of the figure shows the average traffic per \process divided
between $\alpha$ and $\delta$ messages. The bottom part of the figure
shows the time before reaching consistent partitioning.

@@

\noindent Figure~\ref{fig:complexity} shows that the overhead of
adding the $1^{st}$ partition does not correspond to the overhead of
deleting this $1^{st}$ partition. When adding it, messages must reach
all \processes while when removing it, messages must reach a small
subset of this membership. This is important, for it means that
\NAME's overhead actually depends on the current partitioning, and
does not depend on the past partitioning.

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead
when there is no operation in the system. This is important, for it
means that \NAME's overhead actually depends on its usage.

@@

\noindent We evaluate the traffic of \NAME by measuring the average
number of messages per \process over the experiments. In the first
experiment, at $50$ ms, only one \process becomes source, hence there
is only one partition for the whole distributed system. In the second
experiment, at $50$ ms, two \processes become sources, one per
cluster. Afterwards both scenarios are identical. At $500$ ms, we
remove the link between the two clusters. At $1200$ ms, we insert this
link again.

@@

\noindent Figure~\ref{fig:geant} confirms that concurrent \texttt{Add}
may generate additional traffic, for \processes may deliver and forward
a partition only to later realize that they have a closer source.

\noindent Figure~\ref{fig:geant} highlights that removing the
inter-continental link generates additional traffic. The cluster cut
off the source must remove control information about this source. This
generates $\delta$ messages but also $\alpha$ messages, for \NAME
still triggers competitions in the cut off cluster with $\alpha$
messages that monotonically grows until they are purged off the system
by the anti-looping mechanism and corresponding $\delta$s.  Most
importantly, Figure~\ref{fig:geant} shows that \NAME still operates
as expected when \emph{physical} partitions appear. \Processes from the
cluster without source do not belong to any partition while \processes
from the other cluster belong to the same partition.

>>>>

\noindent We focus on the complexity of \NAME. We measure the average
number of messages generated per \process per second during the
experiment; and the time before reaching consistent partitioning after
adding or removing a partition.

@@

Figure~\ref{fig:complexity} shows the results of this experiment. The
top part of the figure shows the average traffic per \process per
second divided between $\alpha$ and $\delta$ messages. The bottom part
of the figure shows the time before reaching consistent partitioning.

@@

\noindent Figure~\ref{fig:complexity} shows that the overhead of
adding the $1^{st}$ partition does not correspond to the overhead of
deleting this $1^{st}$ partition. When adding it, messages must reach
all \processes while when removing it, messages must reach a small
subset of this membership.  \NAME's overhead actually depends on
current partitioning as opposed to past partitionings.

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead
when there is no operation in the system.  \NAME's overhead actually
depends on its usage.

@@

\noindent We evaluate the traffic of \NAME by measuring the average
number of messages per \process over the experiments. In the first
experiment, at $50$~ms, only one \process becomes source, hence there
is only one partition for the whole distributed system. In the second
experiment, at $50$~ms, two \processes become sources, one per
cluster. Afterwards both scenarios are identical. At $850$~ms, we
remove the link between the two clusters. At $1.7$~s, we insert this
link again.

@@

\noindent Figure~\ref{fig:geant} confirms that concurrent
\texttt{Add}s may reach consistent partitioning faster. In particular,
Figure~\ref{fig:geant} depicts a slow down in traffic around $500$ ms
due to the high latency inter-continental link. This link acts as a
bottleneck that does not exist when each cluster has its own source.

\noindent Figure~\ref{fig:geant} highlights that removing the
inter-continental link generates additional traffic. The cluster cut
off from the source must purge all control information about this
source.  Most importantly, Figure~\ref{fig:geant} shows that \NAME
still operates well when \emph{physical} partitions appear. \Processes
from the cluster without source do not belong to any partition while
\processes from the other cluster belong to the same partition.
